Binocular combination in the autonomic nervous system

### 2025-12-18 manuscript.Rmd
Edits

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$*, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
 | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: plos-computational-biology.csl
header-includes:
  \usepackage{caption}
  \usepackage{setspace}\doublespacing
  \usepackage{lineno} \linenumbers
  \newcommand{\beginsupplement}{\setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

# Author Summary

Our pupils constantly adjust in size to control how much light enters the eye: in brighter conditions the pupils will reduce in size, and in dimmer conditions they will increase in size. This process, known as the pupillary light response, is usually taken for granted but is crucial for vision, and is controlled automatically by the body’s nervous system. Different types of light-sensing cells in the retina, the photoreceptor cells, contribute to this response: some respond quickly to changes in light, while others maintain responses over longer periods. In our study, we explored how signals from the two eyes are combined to regulate pupil size. Using a new type of visual stimulation that allowed us to selectively target specific classes of photoreceptor cells, we found that the way the two eyes’ signals are combined depends on which class of photoreceptor cells is involved. For example, some photoreceptor classes showed cooperation between the eyes, while others showed competition. By revealing these distinct patterns of signal combination, our work provides new insight into how light information is integrated in the pupils.

@@

@@

Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41. All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent. Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184).

>>>>

---
title: 'Binocular combination in the autonomic nervous system'
author: |
 | Federico G. Segala$^1$*, Aurelio Bruno$^{1,2}$, Joel T. Martin$^{1,3}$,
 | Anisa Y. Morsi$^1$, Alex R. Wade$^{1,4}$ & Daniel H. Baker$^{1,4}$
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: true
  html_document: default
bibliography: references.bib
link-citations: yes
linkcolor: black
csl: plos-one.csl
header-includes:
  \usepackage{caption}
  \usepackage{setspace}\doublespacing
  \usepackage{lineno} \linenumbers
  \newcommand{\beginsupplement}{\setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

@@

Twenty-four participants were recruited for each of the four experiments for a total of ninety-six adult participants (28 male, 68 female), whose ages ranged from 18 to 41. All participants had normal or corrected to normal vision, no known abnormalities of binocular or colour vision, and gave written informed consent. Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 184). Participant recruitment began on 3 March 2023 and concluded on 8 Decemeber 2023.

@@
